Aspects of RDF Data Constraints in the Social, Behavioural, and Economic Sciences

### 2015-07-20 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
evaluation completes, conclusion

\begin{abstract}
%\boldmath
For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
In this paper, we formulate 213 constraints of 53 different types on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to the complexity level of their type and their severity level. For 115 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
Based on the results, we formulate several hypotheses to direct the further development of constraint languages.\textcolor{red}{81 constraint types instead of 82?}
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

Within the DCMI task group, a collaboratively curated database of RDF validation requirements has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}. It is publicly available and open for further contributions\footnote{Online at \url{http://purl.org/net/rdf-validation}}.
The database connects requirements to use cases, case studies and implementations and forms the basis of this paper. 
We distinguish 82 requirements to formulate RDF constraints; 
each of them corresponding to an RDF constraint type.

@@

A very important and representative RDF validation case study within SBE sciences is the comparison of variables between data collections of different countries.
Several vocabulary-specific constraints on RDF data are checked for each data collection
to determine if variables measuring \emph{age} 
- collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
are comparable:
(1) variable definitions must be available, 
(2) for each code a human-readable label has to be specified,
(3) code lists must be structured properly, and
(4) code lists must either be identical or at least similar.
If a researcher only wants to get a first overview over the comparability of variables (use case 1), 
covering the first three constraints may be sufficient,
i.e., the violation of the first three constraints is more serious than the violation of the last constraint.
If the intention of the researcher is to perform more sophisticated comparisons (use case 2), however, the user may raise the severity level of the last constraint.

@@

%\textbf{Metadata on Person-Level Data.}
For more detailed analyses we refer to the person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}. 
%published by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
Where data collection is cyclic, data sets may be released as \emph{series}, 
where each cycle produces one or more data sets. 
%\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets. 
%This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
%\ke{Wieso jetzt wieder qb?}\tb{ich möchte zeigen wie aggregierte daten und personenbezogene daten in RDF verbunden sind. Weglassen?}
%Aggregated (qb:DataSet) and underlying person-level data sets (\emph{DDI-RDF:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables 
(e.g., \emph{Education at pre-school})
%\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}})
%(2) Education at compulsory school,
%(3) Child care at centre-based services,
%(4) Child care at day-care centre,
%(5) Child care by a professional child-minder, and
%(6) Child care by grand-parents, household members, relatives, friends, neighbours.
for which detailed metadata is given 
%(definitions, descriptions, theoretical concepts, questions variables are based on, code lists, frequencies, descriptive statistics, countries, year of data collection, and classifications) 
(e.g., code lists)
enabling researchers to replicate the results shown in aggregated data tables.
The \emph{DDI-RDF DDI-RDFvery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on person-level data in RDF.
The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
\emph{dcterms:spatial} points to the countries for which the data has been collected.
The study \emph{EU-SILC 2011} contains eight person-level data sets (\emph{DDI-RDF:LogicalDataSet})
including person-level variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
%Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
%One common research question is ,e.g., the comparison of variables like 
%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).

@@

To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types whether they are expressible by different types of constraint languages and on the other hand, we classify concrete constraints formulated for a given vocabulary according to the perceived severity of a violation.

Within the working groups, we identified by today 82 requirements to formulate RDF constraints (e.g., \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}. 
Within a technical report serving as first appendix of this paper we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages \cite{BoschNolleAcarEckert2015}. We provide mappings to representations in description logics (DL) \cite{Baader-2003} to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type.

%In total, we distinguish 82 RDF constraint types as we identified 6 RDF constraint types which are only necessary for validating particular vocabularies.

%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.

The classification of the 115 concrete constraints on three vocabularies according to severity levels is published in a second technical report serving as second appendix of this paper \cite{BoschZapilkoWackerowEckert2015}.
In the following, we summarize the results for the purpose of our evaluation.

@@

According to the expressivity of constraint languages, the complete set of \emph{constraint types} encompasses three not disjoint \emph{sets of constraint types}:
\begin{enumerate}
	\item \emph{RDFS/OWL Based}
	\item \emph{Constraint Language Based}
	\item \emph{SPARQL Based}
\end{enumerate}

The modeling languages RDFS and OWL are typically used to formally specify vocabularies. \emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL constructs using CWA/UNA semantics (without reasoning) and which are therefore commonly found within formal specifications of vocabularies. We determined this set based on the evaluation of the three vocabularies. \emph{RDFS/OWL Based} constraints generally can be seen as a basic level of constraints ensuring that the data is consistent with the formally and explicitly specified intended semantics as well as the integrity of vocabularies' conceptual models about data.

%The {\em existential quantification} (\emph{R-86}) 
%\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (DL), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
Constraints of the constraint type \emph{minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges. In \emph{PHDD}, a \emph{minimum qualified cardinality restriction} can be obtained from a respective OWL axiom which ensures that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
\begin{ex}
[   a owl:Restriction ; rdfs:subClassOf TableStructure ;
    owl:minQualifiedCardinality 1 ;
    owl:onProperty column ;
    owl:onClass Column ] .
\end{ex}

\emph{Constraint Language Based} and \emph{SPARQL Based} constraints are in contrast to \emph{RDFS/OWL Based} constraints usually not (yet) explicitly defined within formal specifications of vocabularies. Instead, they are often defined in textual descriptions of the vocabularies. Additionally, we let our domain and data experts define constraints when they agreed that violating the constraint would affect the usefulness of the data.

We further distinguish \emph{Constraint Language Based} as the set of constraint types that can be expressed by common classical declarative high-level constraint languages like ShEx, ReSh, and DSP. 
%RDFS, and OWL as we consider RDFS and OWL as constraint languages when assuming CWA/UNA semantics without reasoning. 
There is a strong overlap between \emph{RDFS/OWL Based} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by classical constraint languages and OWL. SPARQL, however, is considered as a low-level implementation language in this context, not as a high-level constraint language.

\textcolor{red}{example}

%We further distinguished \emph{simple constraint types} as the set of constraint types whose constraints can be easily defined without much effort in addition to the already defined \emph{vocabulary constraints}.
%\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
%The abstract of series/studies, e.g., should have a minimum length which is easily and concisely expressible by SPARQL: 
%\begin{ex}
%SELECT ?study WHERE {
    %?study dcterms:abstract ?abstract . 
    %FILTER ( STRLEN ( ?abstract ) = 10 ) . }
%\end{ex}
For these constraints, we expect a straight-forward support in future constraint languages.

%\emph{Complex constraint types} encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
\emph{SPARQL Based} encompass constraint types that are not expressible by RDFS/OWL or common constraint languages but by plain SPARQL. For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
An example of such constraints of the constraint type \emph{structure} is that 
a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search. This \emph{complex constraint} is only expressible by SPARQL and not directly understandable:
\begin{ex}
SELECT ?concept WHERE {
    ?concept a [rdfs:subClassOf* skos:Concept] .
    FILTER NOT EXISTS { ?concept ?p ?o . 
        FILTER ( ?p IN ( skos:related, skos:relatedMatch, 
                         skos:broader, ... ) ) . }
\end{ex}
\emph{SPARQL Based} constraint types are today in most cases only expressible by plain SPARQL. Depending on their usefulness, a support in constraint languages should be considered.

@@

A concrete constraint is instantiated from one of the 82 constraint types and is defined for a specific vocabulary.
It does not make sense to determine the severity of constraint violations of an entire constraint type,
as the severity of the violation of a constraint depends on the individual context and vocabulary.
%as the violation of one constraint may be severe,
%whereas, the violation of another constraint of the same type may be minor.
\emph{SBE} experts determined the default \emph{severity level}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}).} for each of the 115 constraints to indicate how serious the violation of the constraint is. We use the classification system of log messages in software development like \emph{Apache Log4j 2} \cite{Apache-2015}, the \emph{Java Logging API}\footnote{\url{http://docs.oracle.com/javase/7/docs/api/java/util/logging/Level.html}}, and the \emph{Apache Commons Logging API}\footnote{\url{http://commons.apache.org/proper/commons-logging/}} as many data practitioners also have experience in software development and software developers intuitively understand these levels. We simplify this commonly accepted classification system and distinguish the three severity levels \emph{informational}, \emph{warning} and \emph{error}.
%According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt... mein vorschlag von eben kann das komplett ersetzen.}
%\begin{itemize}
	%\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
	%\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
	%\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
%\end{itemize}
Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
%They are not seen as serious errors.
\emph{Warnings} are syntactic or semantic problems which typically should not lead to an abortion of data processing.
\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. \textcolor{red}{examples for each in the subsequent section?}
%Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
%Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
%Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation.

Note that there is a correlation between the severity of a constraint and the classification according to the expressivity of constraint languages of its type: \emph{RDFS/OWL Based} constraints are in most cases classified with an \emph{error} level as they typically represent basic and important constraints; there is a reason why they have been included in the vocabulary specification. Although, we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
% Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
% For some use cases, 
% validating \emph{vocabulary constraints} may be more important than validating \emph{simple} or \emph{complex constraints}.
% For other use cases,
% validating \emph{error constraints} may be sufficient without taking \emph{warning} and \emph{informational constraints} into account.
% We evaluated the (meta)data quality of large real world data sets represented by multiple and different vocabularies to get an understanding  
% (1) which sets of constraint types (on different levels of complexity) and 
% (2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).

@@

\textcolor{red}{\emph{Context-specific exclusive or of property groups}} (\emph{R-11}) constraints
restrict individuals of given classes to have properties defined within exactly one of multiple property groups.
\emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both (\emph{error}).

\textcolor{red}{\emph{Default values}} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
The value \emph{true} for the property {\em DDI-RDF:isPublic} indicates that a {\em DDI-RDF:LogicalDataSet} can be accessed by anyone.
Per default, however, access to data sets should be restricted (\emph{false}) ($\mathcal{SL}_{0}$).
Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
The property {\em skos:notation}, e.g., is not mandatory for {\em DDI-RDF:Variable}s, but recommended to represent variable names ($\mathcal{SL}_{0}$).

@@

In a technical report serving as third appendix of this paper, we describe the evaluation in further detail \cite{BoschZapilkoWackerowEckert2015-2}. Furthermore, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.

@@

\textcolor{red}{wurden die severity levels der constraints korrekt ausgezählt?}

@@

Almost 2/3 of all constraints, nearly 1/3 of the DDI-RDF, 60\% of the QB, and all SKOS constraints are \emph{SPARQL Based}. For well-established vocabularies, the most formulated constraints are \emph{SPARQL Based} (80\%). For newly developed vocabularies, however, the most expressed constraints are \emph{RDFS/OWL Based} (2/3). Nearly 80\% of all violations are caused by \emph{SPARQL}, 1/5 by \emph{Constraint Language}, and 1/5 by \emph{RDFS/OWL Based} constraints.
%Hence, a significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
%\begin{hyp}
%As a significant amount of 46 \% of the constraints are vocabulary constraints which can be expressed by modeling languages like RDF, RDFS, and OWL 2,
%the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.   
%As a significant amount of 54\% of the constraints are either simple or complex constraints,
%the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.  
%\end{hyp}
\begin{hyp}
The facts that 80\% of all violations are raised by \emph{SPARQL Based} constraints and that 2/3 of all constraints are SPARQL Based, increases the importance for constraint languages to enable to express SPARQL Based constraints. Thus, the further development of constraint languages especially concentrates on expressing SPARQL Based constraints as data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{SPARQL Based} constraints in an easy, concise, and intuitive way. The more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL. 
\end{hyp}

@@

Nearly 1/3 of all constraints are either \emph{RDFS/OWL} or \emph{Constraint Language Based}.

\begin{hyp}
The first step to make progress in the further development of constraint languages is to cover the constraint types which can already be formulated using RDFS and OWL.
\end{hyp}

>>>>

\begin{abstract}
%\boldmath
For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 81 types of constraints that are required by various stakeholders for data applications.
In this paper, we formulate 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to their severity level and whether their type is expressible by different types of constraint languages. We evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic sciences obtained from 33 SPARQL endpoints.
Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

Within the DCMI task group, a collaboratively curated database of RDF validation requirements has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014} \tb{bibliography error}. It is publicly available and open for further contributions\footnote{Online at \url{http://purl.org/net/rdf-validation}}.
The database connects requirements to use cases, case studies and implementations and forms the basis of this paper. 
We distinguish 81 requirements to formulate RDF constraints; 
each of them corresponding to an RDF constraint type.

@@

A very important and representative RDF validation case study within \emph{SBE} sciences is the comparison of variables between data collections of different countries.
Several vocabulary-specific constraints on RDF data are checked for each data collection
to determine if variables measuring \emph{age} 
- collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
are comparable:
(1) variable definitions must be available, 
(2) for each code a human-readable label has to be specified,
(3) code lists must be structured properly, and
(4) code lists must either be identical or at least similar.
If a researcher only wants to get a first overview over the comparability of variables (use case 1), 
covering the first three constraints may be sufficient,
i.e., the violation of the first three constraints is more serious than the violation of the last constraint.
If the intention of the researcher is to perform more sophisticated comparisons (use case 2), however, the user may raise the severity level of the last constraint.

@@

%\textbf{Metadata on Person-Level Data.}
For more detailed analyses we refer to the person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}. 
%published by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
Where data collection is cyclic, data sets may be released as \emph{series}, 
where each cycle produces one or more data sets. 
%\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets. 
%This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
%\ke{Wieso jetzt wieder qb?}\tb{ich möchte zeigen wie aggregierte daten und personenbezogene daten in RDF verbunden sind. Weglassen?}
%Aggregated (qb:DataSet) and underlying person-level data sets (\emph{DDI-RDF:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables 
(e.g., \emph{Education at pre-school})
%\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}})
%(2) Education at compulsory school,
%(3) Child care at centre-based services,
%(4) Child care at day-care centre,
%(5) Child care by a professional child-minder, and
%(6) Child care by grand-parents, household members, relatives, friends, neighbours.
for which detailed metadata is given 
%(definitions, descriptions, theoretical concepts, questions variables are based on, code lists, frequencies, descriptive statistics, countries, year of data collection, and classifications) 
(e.g., code lists)
enabling researchers to replicate the results shown in aggregated data tables.
The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on person-level data in RDF.
The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
\emph{dcterms:spatial} points to the countries for which the data has been collected.
The study \emph{EU-SILC 2011} contains eight person-level data sets (\emph{DDI-RDF:LogicalDataSet})
including person-level variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
%Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
%One common research question is ,e.g., the comparison of variables like 
%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).

@@

To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types whether they are expressible by different types of constraint languages and on the other hand, we classify constraints formulated for a given vocabulary according to the perceived severity of its violation.

Within the working groups, we identified by today 81 requirements to formulate RDF constraints (e.g., \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}. 
Within a technical report, we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages \cite{BoschNolleAcarEckert2015}. We provide mappings to representations in Description Logics (DL) \cite{Baader-2003} to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type.
%In total, we distinguish 81 RDF constraint types as we identified 6 RDF constraint types which are only necessary for validating particular vocabularies.
%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
The classification of the 115 concrete constraints on three vocabularies according to severity levels is published in a technical report \cite{BoschZapilkoWackerowEckert2015}.
In the following, we summarize the results for the purpose of our evaluation.

@@

According to the expressivity of constraint languages, the complete set of constraint types encompasses three not disjoint sets of constraint types:
\begin{enumerate}
	\item \emph{RDFS/OWL Based}
	\item \emph{Constraint Language Based}
	\item \emph{SPARQL Based}
\end{enumerate}

The modeling languages RDFS and OWL are typically used to formally specify vocabularies. \emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL constructs using CWA/UNA semantics without reasoning and which are therefore commonly found within formal specifications of vocabularies. We determined this set based on the evaluation of the three vocabularies. \emph{RDFS/OWL Based} constraints generally can be seen as a basic level of constraints ensuring that the data is consistent with the formally and explicitly specified intended semantics as well as the integrity of vocabularies' conceptual models about data.

%The {\em existential quantification} (\emph{R-86}) 
%\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (DL), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
Constraints of the constraint type \emph{minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges. For \emph{DDI-RDF}, a \emph{minimum qualified cardinality restriction} can be obtained from a respective OWL axiom which ensures that a \emph{disco:Questionnaire} has (\emph{disco:question}) at least one \emph{disco:Question}:
\begin{ex}
[   a owl:Restriction ; rdfs:subClassOf Questionnaire ;
    owl:minQualifiedCardinality 1 ;
    owl:onProperty question ;
    owl:onClass Question ] .
\end{ex}

%In \emph{PHDD}, a \emph{minimum qualified cardinality restriction} can be obtained from a respective OWL axiom which ensures that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
%\begin{ex}
%[   a owl:Restriction ; rdfs:subClassOf TableStructure ;
    %owl:minQualifiedCardinality 1 ;
    %owl:onProperty column ;
    %owl:onClass Column ] .
%\end{ex}

\emph{Constraint Language Based} and \emph{SPARQL Based} constraints are in contrast to \emph{RDFS/OWL Based} constraints usually not (yet) explicitly defined within formal specifications of vocabularies. Instead, they are often defined within textual descriptions of vocabularies. Additionally, we let our domain and data experts define constraints when they agreed that violating the constraint would affect the usefulness of the data.

We further distinguish \emph{Constraint Language Based} as the set of constraint types that can be expressed by common classical declarative high-level constraint languages like ShEx, ReSh, and DSP. 
%RDFS, and OWL as we consider RDFS and OWL as constraint languages when assuming CWA/UNA semantics without reasoning. 
There is a strong overlap between \emph{RDFS/OWL Based} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by classical constraint languages and OWL. SPARQL, however, is considered as a low-level implementation language in this context. In contrast to SPARQL, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely. Declarative languages may be placed on top of SPARQL when using it as an implementation languages. For these \emph{Constraint Language Based} constraints, we expect a straight-forward support in future constraint languages.

\emph{Context-specific exclusive or of property groups} (\emph{R-11}) is a constraint type which can be formulated by a high-level constraint language. Constraints of this type restrict individuals of given classes to have properties defined within exactly one of multiple mutually exclusive property groups. \emph{skos:Concept}s, e.g., can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both:
%(\emph{error}).

\begin{ex}[commandchars=\\\{\}]
\textit{ShEx:} Concept \{ 
    ( definition string ) |
    ( notation string , prefLabel string ) \}
\end{ex}

%We further distinguished \emph{simple constraint types} as the set of constraint types whose constraints can be easily defined without much effort in addition to the already defined \emph{vocabulary constraints}.
%\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
%The abstract of series/studies, e.g., should have a minimum length which is easily and concisely expressible by SPARQL: 
%\begin{ex}
%SELECT ?study WHERE {
    %?study dcterms:abstract ?abstract . 
    %FILTER ( STRLEN ( ?abstract ) = 10 ) . }
%\end{ex}

%\emph{Complex constraint types} encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
The set \emph{SPARQL Based} encompasses constraint types that are not expressible by RDFS/OWL or common constraint languages but by plain SPARQL. For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
An example of such constraints of the constraint type \emph{structure} is that 
a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search. As the complexity of this constraint is relatively high, it is only expressible by SPARQL and not directly understandable:
\begin{ex}
SELECT ?concept WHERE {
    ?concept a [rdfs:subClassOf* skos:Concept] .
    FILTER NOT EXISTS { ?concept ?p ?o . 
        FILTER ( ?p IN ( skos:related, skos:relatedMatch, 
                         skos:broader, ... ) ) . } }
\end{ex}
\emph{SPARQL Based} constraint types are today in most cases only expressible by plain SPARQL. Depending on their usefulness, a support in constraint languages should be considered.

@@

A concrete constraint is instantiated from one of the 81 constraint types and is defined for a specific vocabulary.
It does not make sense to determine the severity of constraint violations of an entire constraint type,
as the severity of the violation of a constraint depends on the individual context and vocabulary.
%as the violation of one constraint may be severe,
%whereas, the violation of another constraint of the same type may be minor.
\emph{SBE} experts determined the default \emph{severity level}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}).} for each of the 115 constraints to indicate how serious the violation of the constraint is. We use the classification system of log messages in software development like \emph{Apache Log4j 2} \cite{Apache-2015}, the \emph{Java Logging API}\footnote{\url{http://docs.oracle.com/javase/7/docs/api/java/util/logging/Level.html}}, and the \emph{Apache Commons Logging API}\footnote{\url{http://commons.apache.org/proper/commons-logging/}} as many data practitioners also have experience in software development and software developers intuitively understand these levels. We simplify this commonly accepted classification system and distinguish the three severity levels \emph{informational}, \emph{warning} and \emph{error}.
%According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt... mein vorschlag von eben kann das komplett ersetzen.}
%\begin{itemize}
	%\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
	%\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
	%\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
%\end{itemize}
Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
%They are not seen as serious errors.
\emph{Warnings} are syntactic or semantic problems which typically should not lead to an abortion of data processing.
\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. \textcolor{red}{examples for each in the subsequent section?}
%Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
%Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
%Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation.

Note that there is a correlation between the severity of a constraint and the classification according to the expressivity of constraint languages of its type: \emph{RDFS/OWL Based} constraints are in many cases classified with an \emph{error} level as they typically represent basic and important constraints; there is a reason why they have been included in the vocabulary specification. Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity constraints' levels according to their individual needs.
% Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
% For some use cases, 
% validating \emph{vocabulary constraints} may be more important than validating \emph{simple} or \emph{complex constraints}.
% For other use cases,
% validating \emph{error constraints} may be sufficient without taking \emph{warning} and \emph{informational constraints} into account.
% We evaluated the (meta)data quality of large real world data sets represented by multiple and different vocabularies to get an understanding  
% (1) which sets of constraint types (on different levels of complexity) and 
% (2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).

@@

\textcolor{red}{\emph{Default values}} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
The value \emph{true} for the property {\em DDI-RDF:isPublic} indicates that a {\em DDI-RDF:LogicalDataSet} can be accessed by anyone.
Per default, however, access to data sets should be restricted (\emph{false}) (\emph{informational}).
Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
The property {\em skos:notation}, e.g., is not mandatory for {\em DDI-RDF:Variable}s, but recommended to represent variable names (\emph{informational}).

@@

In a technical report, we describe the evaluation in further detail \cite{BoschZapilkoWackerowEckert2015-2}. Furthermore, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.

@@

@@

Almost 2/3 of all constraints, nearly 1/3 of the DDI-RDF, 60\% of the QB, and all SKOS constraints are \emph{SPARQL Based}. For well-established vocabularies, the most formulated constraints are \emph{SPARQL Based} (80\%). For newly developed vocabularies, however, the most expressed constraints are \emph{RDFS/OWL Based} (2/3). Nearly 80\% of all violations are caused by \emph{SPARQL}, 1/5 by \emph{Constraint Language}, and 1/5 by \emph{RDFS/OWL Based} constraints.
%Hence, a significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
%\begin{hyp}
%As a significant amount of 46 \% of the constraints are vocabulary constraints which can be expressed by modeling languages like RDF, RDFS, and OWL 2,
%the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.   
%As a significant amount of 54\% of the constraints are either simple or complex constraints,
%the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.  
%\end{hyp}
\begin{hyp}
The facts that 80\% of all violations are raised by SPARQL Based constraints and that 2/3 of all constraints are SPARQL Based, increases the importance to formulate constraints, which up to now can only be expressed in SPARQL, using high-level constraint languages. Data quality can be significantly improved when suitable constraint languages are developed which enable to define SPARQL Based constraints in an easy, concise, and intuitive way. Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL. 
\end{hyp}

@@

%Nearly 1/3 of all constraints are either \emph{RDFS/OWL} or \emph{Constraint Language Based}.

%The fact that only 1/5 of all violations result from \emph{RDFS/OWL Based} constraints, even though 1/3 of all constraints are \emph{RDFS/OWL Based}, indicates good data quality for all vocabularies with regard to their formal specifications.
